%-------------------------
% Resume in Latex
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}
\usepackage[normalem]{ulem}

\renewcommand{\ULdepth}{1.8pt}
\newcommand{\myuline}[1]{\uline{#1}}

% Helvetica-style font
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}
  {\bfseries\large\raggedright}
  {}
  {0em}
  {}
  [\vspace{1pt}\hrule height 2pt \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2}\vspace{1pt}\\
      \textit{#3} & {\small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Aghilès Gasselin} \\ \vspace{5pt}
    \small 
    \faPhone* \hspace{2pt} \texttt{+31.6.34.69.55.11} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \href{mailto:aghiles.gasselin@gmail.com}{\texttt{aghiles.gasselin@gmail.com}} \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Delft, Netherlands}
    \\ \vspace{3pt}
    \small
    \faLinkedin \hspace{2pt} \href{https://www.linkedin.com/in/aghiles-gasselin/}{\texttt{www.linkedin.com/in/aghiles-gasselin/}}
    \hspace{1pt}$|$\hspace{1pt}
    \faGithub \hspace{2pt} \href{https://github.com/Moa1er}{\texttt{github.com/Moa1er}}
    \\ \vspace{-3pt}
\end{center}

%-----------INTRODUCTION-----------
\section{INTRODUCTION}
\small{
Software Engineering graduate and MSc student in Data Science and Artificial Intelligence at TU Delft, specializing in visual computing, advanced machine learning, and generative modeling. I build AI and software systems across embedded C++, data pipelines, .NET, Angular, SQL, and Azure cloud platforms, with experience in applied AI, bioinformatics research, cyber security, and robotics. Full working rights in Europe and Canada.
}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Delft University of Technology (TU Delft)}{Sep. 2025 -- Jun. 2027}
      {Master in Data Science and Artificial Intelligence}{Delft, Netherlands}
      % \resumeItemListStart
        % \resumeItem{Specialized in \textbf{Visual Computing} and \textbf{Advanced Machine Learning}.}
        % \resumeItem{Projects spanning computer vision, deep learning, perception, and model evaluation.}
      % \resumeItemListEnd

    \resumeSubheading
      {Polytechnic School of Montreal}{Sep. 2019 -- May 2024}
      {Bachelor in Software Engineering}{Montreal, Canada}
      % \resumeItemListStart
        % \resumeItem{Teaching assistant for first-year engineering course in robotics.}
      %   \resumeItem{Active in aerospace committee \textbf{PolyOrbite} and hacking committee \textbf{PolyHx}.}
      % \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------
\section{PROFESSIONAL EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Acquiso inc}{Jan. 2024 -- Aug. 2026}
      {Full Stack \& AI Engineer}{Montreal, Canada}
      \resumeItemListStart
        \resumeItem{Built public-facing marketplace features and internal admin tools using \textbf{Angular}, \textbf{.NET}, \textbf{SQL}, and \textbf{Azure}.}
        \resumeItem{Integrated AI tools for price prediction, multimodal image recognition, and automated text generation using \textbf{regression models} and \textbf{LLMs.}}
        \resumeItem{Optimized platform performance through \textbf{EF Core tuning}, \textbf{server-side caching}, \textbf{lazy loading}, and backend query optimizations.}
      \resumeItemListEnd

    \resumeSubheading
      {Deloitte}{Jun. 2024 -- Jul. 2025}
      {Analyst -- Cyber Defense \& Data Protection}{Montreal, Canada}
      \resumeItemListStart
        \resumeItem{Automated vulnerability intelligence and data gathering using \textbf{XSOAR}, centralizing asset data from \textbf{ServiceNow CMDB} and \textbf{Lansweeper}.}
        \resumeItem{Developed \textbf{Power BI dashboards} to track security risks and support executive decision-making.}
        \resumeItem{Led large-scale data discovery using \textbf{BigID} across \textbf{500+ servers} and billions of files to identify sensitive data and define reduction and retention strategies.}
      \resumeItemListEnd

    \resumeSubheading
      {Korea Advanced Institute of Science \& Technology}{Aug. 2023 -- Dec. 2023}
      {Bioinformatics Research Assistant -- Animal Cell Engineering Laboratory}{Daejeon, South Korea}
      \resumeItemListStart
        \resumeItem{Analyzed genome-scale \textbf{CRISPR knockout screening data} from CHO cells and processed FASTQ sequencing files using \textbf{MAGeCK-VISPR}.}
        \resumeItem{Co-authored an article in \textbf{\textit{Scientific Data} (Nature Portfolio)} on genome-scale CRISPR knockout screening of CHO cells findable \href{https://www.nature.com/articles/s41597-025-04438-6}{\myuline{here}}.}
      \resumeItemListEnd

    \resumeSubheading
      {LABEO Technologies}{May 2022 -- Aug. 2022}
      {Software Engineer Intern}{Montreal, Canada}
      \resumeItemListStart
        \resumeItem{Developed software using \textbf{Qt/C++} and \textbf{Arduino} to automate technical tasks.}
        \resumeItem{Applied algorithmic problem-solving to calculate the weight of mice in an automated system.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages} {: Python, C++, C\#, SQL, TypeScript, JavaScript, Java, Bash}\vspace{2pt} \\
     \textbf{Frameworks \& Libraries} {: .NET, Angular, React, Flutter, Qt, Arduino, EF Core, Power BI}\vspace{2pt} \\
     \textbf{AI \& Machine Learning} {: PyTorch, TensorFlow, NumPy, Pandas, OpenCV, Hugging Face Transformers, LangChain}\vspace{2pt} \\
     \textbf{AI Domains} {: Deep Learning, Computer Vision, Gen AI, LLMs, Reinforcement Learning, Model Evaluation, Bioinformatics}\vspace{2pt} \\
     \textbf{Cloud \& Tools} {: Azure, Git, Jira, JetBrains IDEs, Cursor, XSOAR, ServiceNow CMDB, Lansweeper, BigID}\vspace{2pt} \\
     \textbf{Cyber Security} {: Vulnerability Intelligence, Data Discovery, Data Protection, Retention Strategy, CTF Experience}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{PROJECTS}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\href{https://github.com/Moa1er/Football-Winners}{\textbf{Multi-Camera Multi-Object Tracking for Amateur Football Analytics -- \faGithub}}}{}
      \resumeItemListStart
        \resumeItem{Built a computer vision pipeline to extract player and ball trajectories from \textbf{two synchronized amateur football camera views}.}
        \resumeItem{Fine-tuned \textbf{YOLO26x} on manually labeled football footage using \textbf{Roboflow} and \textbf{Albumentations}, improving small-ball detection under blur and occlusion.}
        \resumeItem{Implemented field registration with \textbf{lens distortion correction}, \textbf{manual point matching}, \textbf{homography estimation}, and reprojection verification using \textbf{OpenCV}.}
        \resumeItem{Combined ByteTrack-based tracking with \textbf{cross-camera fusion}, \textbf{Hungarian matching}, global player IDs, and recovery logic in shared pitch coordinates.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\href{https://github.com/Moa1er/C-JEPA-Reproduction}{\textbf{Causal JEPA Paper Reproduction -- Object-Centric World Model based on JEPA -- \faGithub}}}{}
      \resumeItemListStart
        \resumeItem{Implementing \textbf{latent-space object masking} from scratch, forcing the model to predict masked object states.}
        \resumeItem{Analyzing how \textbf{object-level masking} affects interaction reasoning, temporal prediction, and \textbf{world-model learning}.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\href{https://github.com/Moa1er/FoCAL-reproduction}{\textbf{FoCAL Paper Reproduction -- Prior-Regularized Learned Canonicalization -- \faGithub}}}{}
      \resumeItemListStart
        \resumeItem{Training \textbf{PRLC} models for both \textbf{ResNet50} and \textbf{ViT}, comparing robustness and classification behavior under \textbf{learned canonicalization}.}
        \resumeItem{Extending the project with \textbf{hyperparameter ablation studies} and experiments fitting a \textbf{Spatial Transformer Network (STN)} on top of the PRLC pipeline.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------HOBBIES AND LANGUAGES-----------
\section{HOBBIES \& LANGUAGES}

\begin{minipage}[t]{0.48\textwidth}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Hobbies} \vspace{2pt} \\
     Music: Guitar for 8 years and piano for 3 years \\
     Drone FPV: Building and flying first-person-view drones \\
     Chess and board games
    }}
 \end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages} \vspace{2pt} \\
     French: Native \\
     English: Bilingual, C2 \\
     Korean: Basic, A2
    }}
 \end{itemize}
\end{minipage}

%-------------------------------------------
\end{document}